---
title: "Projection via Monte Carlo Simulation"
author: "Supreme"
output: 
  html_document:
    toc: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
[Previous R Code](/ACTL4001-Supreme/gof) | [Home](/ACTL4001-Supreme) 

```{r, warning=F, message=F, echo=F, eval=TRUE}
rm(list = ls())
graphics.off()
cat("\f")
```

```{r, warning=FALSE, message=FALSE}
# Setting up the environment, load the necessary packages
library(actuar)
library(dplyr)
library(EnvStats)
library(fitdistrplus)
library(kableExtra)
library(knitr)
library(ggplot2)
library(goftest)
library(MASS)
library(readxl)
library(tibble)
library(tidyr)
```

## Loading Data
```{r, warning=FALSE, message=FALSE}
# load data
load(file = "census.RData")
load(file = "emissions.RData")
load(file = "hazards.RData")
load(file = "inflation.RData")
load(file = "rates.RData")
load(file = "prop_dist.RData")

# filtering non-impacting hazards
hazards <- hazards %>% arrange(Year) %>% filter(Property.Damage != 0)
# summarising hazard frequency
frequency <- hazards %>% group_by(Year) %>% summarise(events.pa = n())
```

## Average Aggregate loss in n-years, using MLE Parameters
```{r, warning=F}
options(scipen=999)
set.seed(123)

n_years <- 10 # feel free to adjust: e.g. if you want aggregate loss in 5 years, put n_years <- 5
n_iterations <- 100000 # number of Monte_Carlo simulations: also feel free to adjust.
size <- 1.948557
mu <- 49.704918
shapelog <- 14.829296
ratelog <- 1.413602

sev <- c()

for (i in 1:n_iterations) {
  
  for (i in 1:n_years) {
    freq_vec <- rnbinom(n_years, size = size, mu = mu)
    sev_obs <- sum(rlgamma(freq_vec[i], shapelog = shapelog, ratelog = ratelog))
  }
  
  sev <- append(sev, sev_obs)
  
}

#sanity check: mean aggregate loss in n years / cumulative historical property damages: should be about = n_years / 60
(mean(sev)/sum(hazards$Property.Damage) )
# Previusly we got 0.06579576. For n_years = 10, this should be about 0.1667

# Possible reason for small value: 
# the historical losses include some years where total losses are extreme, which isn't captured by just taking mean(sev)

sev_df <- data.frame(sev)
ggplot(sev_df, aes(x = sev)) + 
    geom_histogram(bins = 100) +
    xlim(c(0, 1000000000)) + ylim(c(0,15000)) +
    ggtitle("Aggregate Loss across Instances") +
    xlab("Aggregate Loss in N Years") +
    ylab("Sample")
```

## Aggregate Loss per year, for each region
### Prep
```{r, warning=FALSE, message=FALSE}
freq1 <- hazards %>% filter(Region == 1) %>% group_by(Year) %>% summarise(events.pa = n())
freq2 <- hazards %>% filter(Region == 2) %>% group_by(Year) %>% summarise(events.pa = n())
freq3 <- hazards %>% filter(Region == 3) %>% group_by(Year) %>% summarise(events.pa = n())
freq4 <- hazards %>% filter(Region == 4) %>% group_by(Year) %>% summarise(events.pa = n())
freq5 <- hazards %>% filter(Region == 5) %>% group_by(Year) %>% summarise(events.pa = n())
freq6 <- hazards %>% filter(Region == 6) %>% group_by(Year) %>% summarise(events.pa = n())

lsev1 <- hazards %>% filter(Region == 1) %>% mutate(Property.Damage = log(Property.Damage))
lsev2 <- hazards %>% filter(Region == 2) %>% mutate(Property.Damage = log(Property.Damage))
lsev3 <- hazards %>% filter(Region == 3) %>% mutate(Property.Damage = log(Property.Damage))
lsev4 <- hazards %>% filter(Region == 4) %>% mutate(Property.Damage = log(Property.Damage))
lsev5 <- hazards %>% filter(Region == 5) %>% mutate(Property.Damage = log(Property.Damage))
lsev6 <- hazards %>% filter(Region == 6) %>% mutate(Property.Damage = log(Property.Damage))

# fit historical frequency per region
nbin1 <- fitdist(freq1$events.pa, "nbinom")
nbin2 <- fitdist(freq2$events.pa, "nbinom")
nbin3 <- fitdist(freq3$events.pa, "nbinom")
nbin4 <- fitdist(freq4$events.pa, "nbinom")
nbin5 <- fitdist(freq5$events.pa, "nbinom")
nbin6 <- fitdist(freq6$events.pa, "nbinom")

# check fit using qq plots
```
```{r, fig.show="hold", out.width="50%", echo=FALSE, warning=FALSE, message=F}
ggplot(freq1, aes(sample = events.pa)) +
    stat_qq(distribution = qnbinom, dparams = c(size = nbin1$estimate[[1]], mu = nbin1$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Negative Binomial Fit: Region 1") +
    xlab("Theoretical") +
    ylab("Empirical")

ggplot(freq2, aes(sample = events.pa)) +
    stat_qq(distribution = qnbinom, dparams = c(size = nbin2$estimate[[1]], mu = nbin2$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Negative Binomial Fit: Region 2") +
    xlab("Theoretical") +
    ylab("Empirical")

ggplot(freq3, aes(sample = events.pa)) +
    stat_qq(distribution = qnbinom, dparams = c(size = nbin3$estimate[[1]], mu = nbin3$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Negative Binomial Fit: Region 3") +
    xlab("Theoretical") +
    ylab("Empirical")

ggplot(freq4, aes(sample = events.pa)) +
    stat_qq(distribution = qnbinom, dparams = c(size = nbin4$estimate[[1]], mu = nbin4$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Negative Binomial Fit: Region 4") +
    xlab("Theoretical") +
    ylab("Empirical")

ggplot(freq5, aes(sample = events.pa)) +
    stat_qq(distribution = qnbinom, dparams = c(size = nbin5$estimate[[1]], mu = nbin5$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Negative Binomial Fit: Region 5") +
    xlab("Theoretical") +
    ylab("Empirical")

ggplot(freq6, aes(sample = events.pa)) +
    stat_qq(distribution = qnbinom, dparams = c(size = nbin6$estimate[[1]], mu = nbin6$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Negative Binomial Fit: Region 6") +
    xlab("Theoretical") +
    ylab("Empirical")
```
`all good!`  

```{r, message=FALSE, warning=FALSE}
# but frequency per year will increase because of climate change
# multiply the mu parameter by each RAF to get a table of different mus, depending on the climate scenario

freq_RAF1 <- emissions %>% mutate(
  SSP1..2.6 = SSP1..2.6*nbin1$estimate[[2]],
  SSP2.3.4 = SSP2.3.4*nbin1$estimate[[2]],
  SSP3.6.0 = SSP3.6.0*nbin1$estimate[[2]],
  SSP5.Baseline = SSP5.Baseline*nbin1$estimate[[2]],
  .keep = "unused"
)
freq_RAF2 <- emissions %>% mutate(
  SSP1..2.6 = SSP1..2.6*nbin2$estimate[[2]],
  SSP2.3.4 = SSP2.3.4*nbin2$estimate[[2]],
  SSP3.6.0 = SSP3.6.0*nbin2$estimate[[2]],
  SSP5.Baseline = SSP5.Baseline*nbin2$estimate[[2]],
  .keep = "unused"
)
freq_RAF3 <- emissions %>% mutate(
  SSP1..2.6 = SSP1..2.6*nbin3$estimate[[2]],
  SSP2.3.4 = SSP2.3.4*nbin3$estimate[[2]],
  SSP3.6.0 = SSP3.6.0*nbin3$estimate[[2]],
  SSP5.Baseline = SSP5.Baseline*nbin3$estimate[[2]],
  .keep = "unused"
)
freq_RAF4 <- emissions %>% mutate(
  SSP1..2.6 = SSP1..2.6*nbin4$estimate[[2]],
  SSP2.3.4 = SSP2.3.4*nbin4$estimate[[2]],
  SSP3.6.0 = SSP3.6.0*nbin4$estimate[[2]],
  SSP5.Baseline = SSP5.Baseline*nbin4$estimate[[2]],
  .keep = "unused"
)
freq_RAF5 <- emissions %>% mutate(
  SSP1..2.6 = SSP1..2.6*nbin5$estimate[[2]],
  SSP2.3.4 = SSP2.3.4*nbin5$estimate[[2]],
  SSP3.6.0 = SSP3.6.0*nbin5$estimate[[2]],
  SSP5.Baseline = SSP5.Baseline*nbin5$estimate[[2]],
  .keep = "unused"
)
freq_RAF6 <- emissions %>% mutate(
  SSP1..2.6 = SSP1..2.6*nbin6$estimate[[2]],
  SSP2.3.4 = SSP2.3.4*nbin6$estimate[[2]],
  SSP3.6.0 = SSP3.6.0*nbin6$estimate[[2]],
  SSP5.Baseline = SSP5.Baseline*nbin6$estimate[[2]],
  .keep = "unused"
)

# fit severity to log-gamma distribution

gamm1 <- fitdist(lsev1$Property.Damage, "gamma")
gamm2 <- fitdist(lsev2$Property.Damage, "gamma")
gamm3 <- fitdist(lsev3$Property.Damage, "gamma")
gamm4 <- fitdist(lsev4$Property.Damage, "gamma")
gamm5 <- fitdist(lsev5$Property.Damage, "gamma")
gamm6 <- fitdist(lsev6$Property.Damage, "gamma")
```
```{r, fig.show="hold", out.width="50%", echo=FALSE, warning=FALSE, message=F}
ggplot(lsev1, aes(sample = Property.Damage)) +
    stat_qq(distribution = qgamma, dparams = c(shape = gamm1$estimate[[1]], rate = gamm1$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Log-Gamma Fit: Region 1") +
    xlab("Theoretical") +
    ylab("Empirical")

ggplot(lsev2, aes(sample = Property.Damage)) +
    stat_qq(distribution = qgamma, dparams = c(shape = gamm2$estimate[[1]], rate = gamm2$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Log-Gamma Fit: Region 2") +
    xlab("Theoretical") +
    ylab("Empirical")

ggplot(lsev3, aes(sample = Property.Damage)) +
    stat_qq(distribution = qgamma, dparams = c(shape = gamm3$estimate[[1]], rate = gamm3$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Log-Gamma Fit: Region 3") +
    xlab("Theoretical") +
    ylab("Empirical")

ggplot(lsev4, aes(sample = Property.Damage)) +
    stat_qq(distribution = qgamma, dparams = c(shape = gamm4$estimate[[1]], rate = gamm4$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Log-Gamma Fit: Region 4") +
    xlab("Theoretical") +
    ylab("Empirical")

ggplot(lsev5, aes(sample = Property.Damage)) +
    stat_qq(distribution = qgamma, dparams = c(shape = gamm5$estimate[[1]], rate = gamm5$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Log-Gamma Fit: Region 5") +
    xlab("Theoretical") +
    ylab("Empirical")

ggplot(lsev6, aes(sample = Property.Damage)) +
    stat_qq(distribution = qgamma, dparams = c(shape = gamm6$estimate[[1]], rate = gamm6$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Log-Gamma Fit: Region 6") +
    xlab("Theoretical") +
    ylab("Empirical")
```

### Simulation
```{r, message=FALSE, warning=F}
n_iterations <- 10000 #number of Monte_Carlo simulations: 

# create empty vector for each region
sev1 <- c()
sev2 <- c()
sev3 <- c()
sev4 <- c()
sev5 <- c()
sev6 <- c()

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin1$estimate[[1]], mu = nbin1$estimate[[2]])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm1$estimate[[1]], rate = gamm1$estimate[[2]])))
  sev1 <- append(sev1, sev_pa)
}

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin2$estimate[[1]], mu = nbin2$estimate[[2]])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm2$estimate[[1]], rate = gamm2$estimate[[2]])))
  sev2 <- append(sev2, sev_pa)
}

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin3$estimate[[1]], mu = nbin3$estimate[[2]])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm3$estimate[[1]], rate = gamm3$estimate[[2]])))
  sev3 <- append(sev3, sev_pa)
}

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin4$estimate[[1]], mu = nbin4$estimate[[2]])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm4$estimate[[1]], rate = gamm4$estimate[[2]])))
  sev4 <- append(sev4, sev_pa)
}

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin5$estimate[[1]], mu = nbin5$estimate[[2]])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm5$estimate[[1]], rate = gamm5$estimate[[2]])))
  sev5 <- append(sev5, sev_pa)
}

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin6$estimate[[1]], mu = nbin6$estimate[[2]])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm6$estimate[[1]], rate = gamm6$estimate[[2]])))
  sev6 <- append(sev6, sev_pa)
}

# convert the filled in vector through iterations to dataframe
sev1_df <- data.frame(sev1)
sev2_df <- data.frame(sev2)
sev3_df <- data.frame(sev3)
sev4_df <- data.frame(sev4)
sev5_df <- data.frame(sev5)
sev6_df <- data.frame(sev6)

# such that we have the aggregate loss of each region for the following year as below
```
```{r, fig.show="hold", out.width="50%", echo=FALSE, warning=FALSE, message=F}

ggplot(sev1_df, aes(x = sev1)) + 
    geom_histogram(bins = 100) +
    xlim(c(0, 1e+09)) +
    ggtitle("Aggregate Loss across Instances in Region 1") +
    xlab("Aggregate Loss in 1 Year") +
    ylab("Count")

ggplot(sev2_df, aes(x = sev2)) + 
    geom_histogram(bins = 100) +
    xlim(c(0, 1e+09)) +
    ggtitle("Aggregate Loss across Instances in Region 2") +
    xlab("Aggregate Loss in 1 Year") +
    ylab("Count")

ggplot(sev3_df, aes(x = sev3)) + 
    geom_histogram(bins = 100) +
    xlim(c(0, 1e+09)) +
    ggtitle("Aggregate Loss across Instances in Region 3") +
    xlab("Aggregate Loss in 1 Year") +
    ylab("Count")

ggplot(sev4_df, aes(x = sev4)) + 
    geom_histogram(bins = 100) +
    xlim(c(0, 1e+09)) +
    ggtitle("Aggregate Loss across Instances in Region 4") +
    xlab("Aggregate Loss in 1 Year") +
    ylab("Count")

ggplot(sev5_df, aes(x = sev5)) + 
    geom_histogram(bins = 100) +
    xlim(c(0, 1e+09)) +
    ggtitle("Aggregate Loss across Instances in Region 5") +
    xlab("Aggregate Loss in 1 Year") +
    ylab("Count")

ggplot(sev6_df, aes(x = sev6)) + 
    geom_histogram(bins = 100) +
    xlim(c(0, 1e+09)) +
    ggtitle("Aggregate Loss across Instances in Region 6") +
    xlab("Aggregate Loss in 1 Years") +
    ylab("Count")
```

### Value at Risk
```{r, message=FALSE, warning=FALSE}
#Percentiles: help compute VaR
perc <- c(0.25, 0.5, 0.75, 0.8, 0.85, 0.9, 0.95, 0.98, 0.99, 0.995, 0.999)
Percentile <- c(perc, "Mean", "SD", "Max")
gross1 <- c(quantile(sev1, probs = perc), mean(sev1), sd(sev1), max(sev1))
gross2 <- c(quantile(sev2, probs = perc), mean(sev2), sd(sev2), max(sev2))
gross3 <- c(quantile(sev3, probs = perc), mean(sev3), sd(sev3), max(sev3))
gross4 <- c(quantile(sev4, probs = perc), mean(sev4), sd(sev4), max(sev4))
gross5 <- c(quantile(sev5, probs = perc), mean(sev5), sd(sev5), max(sev5))
gross6 <- c(quantile(sev6, probs = perc), mean(sev6), sd(sev6), max(sev6))

results.table <- data.frame(Percentile, gross1, gross2, gross3, gross4, gross5, gross6)
# gross stands for the possible loss at the respective percentile
kable(results.table) %>%
  kable_styling(full_width = F)

# if we look at the historical property damage

hazards_sorted <- hazards %>% group_by(Year) %>% summarise(sum(Property.Damage))
head(hazards_sorted, 10)

# seems to underestimate aggregate loss
# may need to either exclude older years, or adjust damages for inflation
```

## Incorporating Inflation
```{r, warning=FALSE, message=FALSE}
# formating the data for use
inflation = as.data.frame(inflation) %>% 
  remove_rownames %>% 
  column_to_rownames(var="Year")

# Data of inflation starts from 1962, we omit data before year 1962
hazards_adj <- hazards %>%
  dplyr::filter(Year >= 1962)

# reiterating the steps above with inflation incorporated
for (i in 1:nrow(hazards_adj)) {
  hazards_adj$Property.Damage[i] = hazards_adj$Property.Damage[i] * inflation$FV[rownames(inflation) == as.character(hazards_adj$Year[i])]
}

hazards <- hazards_adj

freq1 <- hazards %>% filter(Region == 1) %>% group_by(Year) %>% summarise(events.pa = n())
freq2 <- hazards %>% filter(Region == 2) %>% group_by(Year) %>% summarise(events.pa = n())
freq3 <- hazards %>% filter(Region == 3) %>% group_by(Year) %>% summarise(events.pa = n())
freq4 <- hazards %>% filter(Region == 4) %>% group_by(Year) %>% summarise(events.pa = n())
freq5 <- hazards %>% filter(Region == 5) %>% group_by(Year) %>% summarise(events.pa = n())
freq6 <- hazards %>% filter(Region == 6) %>% group_by(Year) %>% summarise(events.pa = n())

lsev1 <- hazards %>% filter(Region == 1) %>% mutate(Property.Damage = log(Property.Damage))
lsev2 <- hazards %>% filter(Region == 2) %>% mutate(Property.Damage = log(Property.Damage))
lsev3 <- hazards %>% filter(Region == 3) %>% mutate(Property.Damage = log(Property.Damage))
lsev4 <- hazards %>% filter(Region == 4) %>% mutate(Property.Damage = log(Property.Damage))
lsev5 <- hazards %>% filter(Region == 5) %>% mutate(Property.Damage = log(Property.Damage))
lsev6 <- hazards %>% filter(Region == 6) %>% mutate(Property.Damage = log(Property.Damage))

# fit historical frequency per region
nbin1 <- fitdist(freq1$events.pa, "nbinom")
nbin2 <- fitdist(freq2$events.pa, "nbinom")
nbin3 <- fitdist(freq3$events.pa, "nbinom")
nbin4 <- fitdist(freq4$events.pa, "nbinom")
nbin5 <- fitdist(freq5$events.pa, "nbinom")
nbin6 <- fitdist(freq6$events.pa, "nbinom")

# check fit using qq plots
```
```{r, fig.show="hold", out.width="50%", echo=FALSE, warning=FALSE, message=F}
ggplot(freq1, aes(sample = events.pa)) +
    stat_qq(distribution = qnbinom, dparams = c(size = nbin1$estimate[[1]], mu = nbin1$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Negative Binomial Fit: Region 1") +
    xlab("Theoretical") +
    ylab("Empirical")

ggplot(freq2, aes(sample = events.pa)) +
    stat_qq(distribution = qnbinom, dparams = c(size = nbin2$estimate[[1]], mu = nbin2$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Negative Binomial Fit: Region 2") +
    xlab("Theoretical") +
    ylab("Empirical")

ggplot(freq3, aes(sample = events.pa)) +
    stat_qq(distribution = qnbinom, dparams = c(size = nbin3$estimate[[1]], mu = nbin3$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Negative Binomial Fit: Region 3") +
    xlab("Theoretical") +
    ylab("Empirical")

ggplot(freq4, aes(sample = events.pa)) +
    stat_qq(distribution = qnbinom, dparams = c(size = nbin4$estimate[[1]], mu = nbin4$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Negative Binomial Fit: Region 4") +
    xlab("Theoretical") +
    ylab("Empirical")

ggplot(freq5, aes(sample = events.pa)) +
    stat_qq(distribution = qnbinom, dparams = c(size = nbin5$estimate[[1]], mu = nbin5$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Negative Binomial Fit: Region 5") +
    xlab("Theoretical") +
    ylab("Empirical")

ggplot(freq6, aes(sample = events.pa)) +
    stat_qq(distribution = qnbinom, dparams = c(size = nbin6$estimate[[1]], mu = nbin6$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Negative Binomial Fit: Region 6") +
    xlab("Theoretical") +
    ylab("Empirical")
```
`looks all good!`  

```{r, message=FALSE, warning=FALSE}
# multiply the mu parameter by each RAF to get a table of different mus, depending on the climate scenario

freq_RAF1 <- emissions %>% mutate(
  SSP1..2.6 = SSP1..2.6*nbin1$estimate[[2]],
  SSP2.3.4 = SSP2.3.4*nbin1$estimate[[2]],
  SSP3.6.0 = SSP3.6.0*nbin1$estimate[[2]],
  SSP5.Baseline = SSP5.Baseline*nbin1$estimate[[2]],
  .keep = "unused"
)
freq_RAF2 <- emissions %>% mutate(
  SSP1..2.6 = SSP1..2.6*nbin2$estimate[[2]],
  SSP2.3.4 = SSP2.3.4*nbin2$estimate[[2]],
  SSP3.6.0 = SSP3.6.0*nbin2$estimate[[2]],
  SSP5.Baseline = SSP5.Baseline*nbin2$estimate[[2]],
  .keep = "unused"
)
freq_RAF3 <- emissions %>% mutate(
  SSP1..2.6 = SSP1..2.6*nbin3$estimate[[2]],
  SSP2.3.4 = SSP2.3.4*nbin3$estimate[[2]],
  SSP3.6.0 = SSP3.6.0*nbin3$estimate[[2]],
  SSP5.Baseline = SSP5.Baseline*nbin3$estimate[[2]],
  .keep = "unused"
)
freq_RAF4 <- emissions %>% mutate(
  SSP1..2.6 = SSP1..2.6*nbin4$estimate[[2]],
  SSP2.3.4 = SSP2.3.4*nbin4$estimate[[2]],
  SSP3.6.0 = SSP3.6.0*nbin4$estimate[[2]],
  SSP5.Baseline = SSP5.Baseline*nbin4$estimate[[2]],
  .keep = "unused"
)
freq_RAF5 <- emissions %>% mutate(
  SSP1..2.6 = SSP1..2.6*nbin5$estimate[[2]],
  SSP2.3.4 = SSP2.3.4*nbin5$estimate[[2]],
  SSP3.6.0 = SSP3.6.0*nbin5$estimate[[2]],
  SSP5.Baseline = SSP5.Baseline*nbin5$estimate[[2]],
  .keep = "unused"
)
freq_RAF6 <- emissions %>% mutate(
  SSP1..2.6 = SSP1..2.6*nbin6$estimate[[2]],
  SSP2.3.4 = SSP2.3.4*nbin6$estimate[[2]],
  SSP3.6.0 = SSP3.6.0*nbin6$estimate[[2]],
  SSP5.Baseline = SSP5.Baseline*nbin6$estimate[[2]],
  .keep = "unused"
)

# similarly also fit severity to log-gamma distribution

gamm1 <- fitdist(lsev1$Property.Damage, "gamma")
gamm2 <- fitdist(lsev2$Property.Damage, "gamma")
gamm3 <- fitdist(lsev3$Property.Damage, "gamma")
gamm4 <- fitdist(lsev4$Property.Damage, "gamma")
gamm5 <- fitdist(lsev5$Property.Damage, "gamma")
gamm6 <- fitdist(lsev6$Property.Damage, "gamma")
```
```{r, fig.show="hold", out.width="50%", echo=FALSE, warning=FALSE, message=F}
ggplot(lsev1, aes(sample = Property.Damage)) +
    stat_qq(distribution = qgamma, dparams = c(shape = gamm1$estimate[[1]], rate = gamm1$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Log-Gamma Fit: Region 1") +
    xlab("Theoretical") +
    ylab("Empirical")

ggplot(lsev2, aes(sample = Property.Damage)) +
    stat_qq(distribution = qgamma, dparams = c(shape = gamm2$estimate[[1]], rate = gamm2$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Log-Gamma Fit: Region 2") +
    xlab("Theoretical") +
    ylab("Empirical")

ggplot(lsev3, aes(sample = Property.Damage)) +
    stat_qq(distribution = qgamma, dparams = c(shape = gamm3$estimate[[1]], rate = gamm3$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Log-Gamma Fit: Region 3") +
    xlab("Theoretical") +
    ylab("Empirical")

ggplot(lsev4, aes(sample = Property.Damage)) +
    stat_qq(distribution = qgamma, dparams = c(shape = gamm4$estimate[[1]], rate = gamm4$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Log-Gamma Fit: Region 4") +
    xlab("Theoretical") +
    ylab("Empirical")

ggplot(lsev5, aes(sample = Property.Damage)) +
    stat_qq(distribution = qgamma, dparams = c(shape = gamm5$estimate[[1]], rate = gamm5$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Log-Gamma Fit: Region 5") +
    xlab("Theoretical") +
    ylab("Empirical")

ggplot(lsev6, aes(sample = Property.Damage)) +
    stat_qq(distribution = qgamma, dparams = c(shape = gamm6$estimate[[1]], rate = gamm6$estimate[[2]]), colour = "#00BFC4", size = 1) +
    geom_abline(slope=1, intercept = 0) +
    theme_bw() +
    theme(axis.title = element_text(size = 13.5)) +
    ggtitle("Log-Gamma Fit: Region 6") +
    xlab("Theoretical") +
    ylab("Empirical")
```

### Inflation adjusted simulation 
```{r, warning=FALSE, message=FALSE}
n_iterations <- 10000 #number of Monte_Carlo simulations: 

sev1 <- c()
sev2 <- c()
sev3 <- c()
sev4 <- c()
sev5 <- c()
sev6 <- c()
sev_agg <- numeric(n_iterations)

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin1$estimate[[1]], mu = nbin1$estimate[[2]])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm1$estimate[[1]], rate = gamm1$estimate[[2]])))
  sev1 <- append(sev1, sev_pa)
  sev_agg[i] = sev_agg[i] + sev_pa
}

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin2$estimate[[1]], mu = nbin2$estimate[[2]])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm2$estimate[[1]], rate = gamm2$estimate[[2]])))
  sev2 <- append(sev2, sev_pa)
  sev_agg[i] = sev_agg[i] + sev_pa
}

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin3$estimate[[1]], mu = nbin3$estimate[[2]])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm3$estimate[[1]], rate = gamm3$estimate[[2]])))
  sev3 <- append(sev3, sev_pa)
  sev_agg[i] = sev_agg[i] + sev_pa
}

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin4$estimate[[1]], mu = nbin4$estimate[[2]])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm4$estimate[[1]], rate = gamm4$estimate[[2]])))
  sev4 <- append(sev4, sev_pa)
  sev_agg[i] = sev_agg[i] + sev_pa
}

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin5$estimate[[1]], mu = nbin5$estimate[[2]])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm5$estimate[[1]], rate = gamm5$estimate[[2]])))
  sev5 <- append(sev5, sev_pa)
  sev_agg[i] = sev_agg[i] + sev_pa
}

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin6$estimate[[1]], mu = nbin6$estimate[[2]])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm6$estimate[[1]], rate = gamm6$estimate[[2]])))
  sev6 <- append(sev6, sev_pa)
  sev_agg[i] = sev_agg[i] + sev_pa
}
  
sev1_df <- data.frame(sev1)
sev2_df <- data.frame(sev2)
sev3_df <- data.frame(sev3)
sev4_df <- data.frame(sev4)
sev5_df <- data.frame(sev5)
sev6_df <- data.frame(sev6)
agg_df <- data.frame(sev_agg)

# such that we have the aggregate loss of each region for the following year as below
```
```{r, fig.show="hold", out.width="50%", echo=FALSE, warning=FALSE, message=F}

ggplot(sev1_df, aes(x = sev1)) + 
    geom_histogram(bins = 100) +
    xlim(c(0, 1e+09)) +
    ggtitle("Aggregate Loss across Instances in Region 1") +
    xlab("Aggregate Loss in 1 Year") +
    ylab("Count")

ggplot(sev2_df, aes(x = sev2)) + 
    geom_histogram(bins = 100) +
    xlim(c(0, 1e+09)) +
    ggtitle("Aggregate Loss across Instances in Region 2") +
    xlab("Aggregate Loss in 1 Year") +
    ylab("Count")

ggplot(sev3_df, aes(x = sev3)) + 
    geom_histogram(bins = 100) +
    xlim(c(0, 1e+09)) +
    ggtitle("Aggregate Loss across Instances in Region 3") +
    xlab("Aggregate Loss in 1 Year") +
    ylab("Count")

ggplot(sev4_df, aes(x = sev4)) + 
    geom_histogram(bins = 100) +
    xlim(c(0, 1e+09)) +
    ggtitle("Aggregate Loss across Instances in Region 4") +
    xlab("Aggregate Loss in 1 Year") +
    ylab("Count")

ggplot(sev5_df, aes(x = sev5)) + 
    geom_histogram(bins = 100) +
    xlim(c(0, 1e+09)) +
    ggtitle("Aggregate Loss across Instances in Region 5") +
    xlab("Aggregate Loss in 1 Year") +
    ylab("Count")

ggplot(sev6_df, aes(x = sev6)) + 
    geom_histogram(bins = 100) +
    xlim(c(0, 1e+09)) +
    ggtitle("Aggregate Loss across Instances in Region 6") +
    xlab("Aggregate Loss in 1 Years") +
    ylab("Count")
```

### Value at Risk
```{r, message=FALSE, warning=FALSE}
#Percentiles: help compute VaR
perc <- c(0.25, 0.5, 0.75, 0.8, 0.85, 0.9, 0.95, 0.98, 0.99, 0.995, 0.999)
Percentile <- c(perc, "Mean", "SD", "Max")
gross1 <- c(quantile(sev1, probs = perc), mean(sev1), sd(sev1), max(sev1))
gross2 <- c(quantile(sev2, probs = perc), mean(sev2), sd(sev2), max(sev2))
gross3 <- c(quantile(sev3, probs = perc), mean(sev3), sd(sev3), max(sev3))
gross4 <- c(quantile(sev4, probs = perc), mean(sev4), sd(sev4), max(sev4))
gross5 <- c(quantile(sev5, probs = perc), mean(sev5), sd(sev5), max(sev5))
gross6 <- c(quantile(sev6, probs = perc), mean(sev6), sd(sev6), max(sev6))

results.table <- data.frame(Percentile, gross1, gross2, gross3, gross4, gross5, gross6)
# gross stands for the possible loss at the respective percentile
kable(results.table) %>%
  kable_styling(full_width = F)

# if we look at the historical property damage

hazards_sorted <- hazards %>% group_by(Year) %>% summarise(sum(Property.Damage))
head(hazards_sorted, 10)

# comparing the empirical and projected aggregate loss per region
emp_df1 <- data.frame(group = "emp", value = lsev1$Property.Damage)
emp_df2 <- data.frame(group = "emp", value = lsev2$Property.Damage)
emp_df3 <- data.frame(group = "emp", value = lsev3$Property.Damage)
emp_df4 <- data.frame(group = "emp", value = lsev4$Property.Damage)
emp_df5 <- data.frame(group = "emp", value = lsev5$Property.Damage)
emp_df6 <- data.frame(group = "emp", value = lsev6$Property.Damage)
emp_df <- data.frame(group = "emp", value = log(hazards_sorted$`sum(Property.Damage)`))

proj_df1 <- data.frame(group = "proj", value = log(sev1_df$sev1))
proj_df2 <- data.frame(group = "proj", value = log(sev2_df$sev2))
proj_df3 <- data.frame(group = "proj", value = log(sev3_df$sev3))
proj_df4 <- data.frame(group = "proj", value = log(sev4_df$sev4))
proj_df5 <- data.frame(group = "proj", value = log(sev5_df$sev5))
proj_df6 <- data.frame(group = "proj", value = log(sev6_df$sev6))
proj_df <- data.frame(group = "proj", value = log(agg_df$sev_agg))
```
```{r, fig.show="hold", out.width="33.33%", echo=FALSE, warning=FALSE, message=F}

plot_data = rbind(emp_df1,proj_df1)
(ggplot(plot_data, aes(x=group, y=value, fill=group)) + 
    geom_boxplot() + 
    ggtitle("Aggregate Yearly Loss Projection 1"))
 
plot_data = rbind(emp_df2,proj_df2)
(ggplot(plot_data, aes(x=group, y=value, fill=group)) + 
    geom_boxplot() + 
    ggtitle("Aggregate Yearly Loss Projection 2"))
  
plot_data = rbind(emp_df3,proj_df3)
(ggplot(plot_data, aes(x=group, y=value, fill=group)) + 
    geom_boxplot() + 
    ggtitle("Aggregate Yearly Loss Projection 3"))

plot_data = rbind(emp_df4,proj_df4)
(ggplot(plot_data, aes(x=group, y=value, fill=group)) + 
    geom_boxplot() + 
    ggtitle("Aggregate Yearly Loss Projection 4"))

plot_data = rbind(emp_df5,proj_df5)
(ggplot(plot_data, aes(x=group, y=value, fill=group)) + 
    geom_boxplot() + 
    ggtitle("Aggregate Yearly Loss Projection 5"))

plot_data = rbind(emp_df6,proj_df6)
(ggplot(plot_data, aes(x=group, y=value, fill=group)) + 
    geom_boxplot() + 
    ggtitle("Aggregate Yearly Loss Projection 6"))

plot_data = rbind(emp_df,proj_df)
(ggplot(plot_data, aes(x=group, y=value, fill=group)) + 
  geom_boxplot() + 
  ggtitle("Aggregate Yearly Loss Projection (taking climate into considerartion)"))
```
> seems to underestimate aggregate loss.  
> may need to either exclude older years, or adjust damages for inflation. 

## Program Loss
**Assumptions**

  * Property are equally likely to be injured
  
  * Material and Labour costs increment follow uniform distribution ~ U(0, 0.5)
  
  * The cost of replacing Household goods follow uniform distribution ~ U(0.4, 0.75)

```{r, message=FALSE, warning=FALSE}

# Set up parameters
n_iterations <- 10000 # number of Monte_Carlo simulations: 
set.seed(123)
mat_increase <- runif(n_iterations, 0,0.5)
hh_cost <- runif(n_iterations, 0.4, 0.75)
```

### Short-term Program Cost Projection 
```{r, warning=FALSE, message=FALSE}
# We omit region 5 and 6 as they are low-risk region and would not relocate under our program design
loss1 <- c()
loss2 <- c()
loss3 <- c()
loss4 <- c()
loss_agg <- numeric(n_iterations)

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin1$estimate[[1]], mu = nbin1$estimate[[2]])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm1$estimate[[1]], rate = gamm1$estimate[[2]])))
  loss <- sev_pa * (1 + mat_increase[i]) * (1 + hh_cost[i])* prop_dist[1,1]
  loss1 <- append(loss1,loss)
  loss_agg[i] = loss_agg[i] + loss
}

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin2$estimate[[1]], mu = nbin2$estimate[[2]])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm2$estimate[[1]], rate = gamm2$estimate[[2]])))
  loss <- sev_pa * (1 + mat_increase[i]) * (1 + hh_cost[i])* prop_dist[2,1]
  loss2 <- append(loss2,loss)
  loss_agg[i] = loss_agg[i] + loss
}

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin3$estimate[[1]], mu = nbin3$estimate[[2]])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm3$estimate[[1]], rate = gamm3$estimate[[2]])))
  loss <- sev_pa * (1 + mat_increase[i]) * (1 + hh_cost[i])* prop_dist[3,1]
  loss3 <- append(loss3,loss)
  loss_agg[i] = loss_agg[i] + loss
}

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin4$estimate[[1]], mu = nbin4$estimate[[2]])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm4$estimate[[1]], rate = gamm4$estimate[[2]])))
  loss <- sev_pa * (1 + mat_increase[i]) * (1 + hh_cost[i])* prop_dist[4,1]
  loss4 <- append(loss4,loss)
  loss_agg[i] = loss_agg[i] + loss
}

perc <- c(0.25, 0.5, 0.75, 0.8, 0.85, 0.9, 0.95, 0.98, 0.99, 0.995, 0.999)
Percentile <- c(perc, "Mean", "SD", "Max")
gross1 <- c(quantile(loss1, probs = perc), mean(loss1), sd(loss1), max(loss1))
gross2 <- c(quantile(loss2, probs = perc), mean(loss2), sd(loss2), max(loss2))
gross3 <- c(quantile(loss3, probs = perc), mean(loss3), sd(loss3), max(loss3))
gross4 <- c(quantile(loss4, probs = perc), mean(loss4), sd(loss4), max(loss4))

results.table2 <- data.frame(Percentile, gross1, gross2, gross3, gross4)
kable(results.table2) %>%
  kable_styling(full_width = F)
```

### Long-term Loss Projection (2030)
```{r, message=FALSE, warning=FALSE}
sev1 <- c()
sev2 <- c()
sev3 <- c()
sev4 <- c()
sev5 <- c()
sev6 <- c()
sev_agg <- numeric(n_iterations)


for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin1$estimate[[1]], mu = freq_RAF1[2,4])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm1$estimate[[1]], rate = gamm1$estimate[[2]])))
  sev1 <- append(sev1, sev_pa)
  sev_agg[i] = sev_agg[i] + sev_pa
}

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin2$estimate[[1]], mu = freq_RAF2[2,4])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm2$estimate[[1]], rate = gamm2$estimate[[2]])))
  sev2 <- append(sev2, sev_pa)
  sev_agg[i] = sev_agg[i] + sev_pa
}

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin3$estimate[[1]], mu = freq_RAF3[2,4])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm3$estimate[[1]], rate = gamm3$estimate[[2]])))
  sev3 <- append(sev3, sev_pa)
  sev_agg[i] = sev_agg[i] + sev_pa
}

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin4$estimate[[1]], mu = freq_RAF4[2,4])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm4$estimate[[1]], rate = gamm4$estimate[[2]])))
  sev4 <- append(sev4, sev_pa)
  sev_agg[i] = sev_agg[i] + sev_pa
}

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin5$estimate[[1]], mu = freq_RAF5[2,4])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm5$estimate[[1]], rate = gamm5$estimate[[2]])))
  sev5 <- append(sev5, sev_pa)
  sev_agg[i] = sev_agg[i] + sev_pa
}

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin6$estimate[[1]], mu = freq_RAF6[2,4])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm6$estimate[[1]], rate = gamm6$estimate[[2]])))
  sev6 <- append(sev6, sev_pa)
  sev_agg[i] = sev_agg[i] + sev_pa
}

sev1_df <- data.frame(sev1)
sev2_df <- data.frame(sev2)
sev3_df <- data.frame(sev3)
sev4_df <- data.frame(sev4)
sev5_df <- data.frame(sev5)
sev6_df <- data.frame(sev6)
agg_df <- data.frame(sev_agg)

perc <- c(0.25, 0.5, 0.75, 0.8, 0.85, 0.9, 0.95, 0.98, 0.99, 0.995, 0.999)
Percentile <- c(perc, "Mean", "SD", "Max")
gross1 <- c(quantile(sev1, probs = perc), mean(sev1), sd(sev1), max(sev1))
gross2 <- c(quantile(sev2, probs = perc), mean(sev2), sd(sev2), max(sev2))
gross3 <- c(quantile(sev3, probs = perc), mean(sev3), sd(sev3), max(sev3))
gross4 <- c(quantile(sev4, probs = perc), mean(sev4), sd(sev4), max(sev4))
gross5 <- c(quantile(sev5, probs = perc), mean(sev5), sd(sev5), max(sev5))
gross6 <- c(quantile(sev6, probs = perc), mean(sev6), sd(sev6), max(sev6))

results.table3 <- data.frame(Percentile, gross1, gross2, gross3, gross4, gross5, gross6)
kable(results.table3) %>%
  kable_styling(full_width = F)
```

### Long-term Program Cost Projection
```{r, message=FALSE, warning=FALSE}
mat_increase <- runif(n_iterations, 0,0.5)
hh_cost <- runif(n_iterations, 0.4, 0.75)

loss1 <- c()
loss2 <- c()
loss3 <- c()
loss4 <- c()
loss_agg <- numeric(n_iterations)

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin1$estimate[[1]], mu = freq_RAF1[2,4])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm1$estimate[[1]], rate = gamm1$estimate[[2]])))
  loss <- sev_pa * (1 + mat_increase[i]) * (1 + hh_cost[i])* prop_dist[1,1]
  loss1 <- append(loss1,loss)
  loss_agg[i] = loss_agg[i] + loss
}

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin2$estimate[[1]], mu = freq_RAF2[2,4])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm2$estimate[[1]], rate = gamm2$estimate[[2]])))
  loss <- sev_pa * (1 + mat_increase[i]) * (1 + hh_cost[i])* prop_dist[2,1]
  loss2 <- append(loss2,loss)
  loss_agg[i] = loss_agg[i] + loss
}

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin3$estimate[[1]], mu = freq_RAF3[2,4])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm3$estimate[[1]], rate = gamm3$estimate[[2]])))
  loss <- sev_pa * (1 + mat_increase[i]) * (1 + hh_cost[i])* prop_dist[3,1]
  loss3 <- append(loss3,loss)
  loss_agg[i] = loss_agg[i] + loss
}

for (i in 1:n_iterations) {
  freq_vec <- rnbinom(1, size = nbin4$estimate[[1]], mu = freq_RAF4[2,4])
  sev_pa <- sum(exp(rgamma(freq_vec, shape = gamm4$estimate[[1]], rate = gamm4$estimate[[2]])))
  loss <- sev_pa * (1 + mat_increase[i]) * (1 + hh_cost[i])* prop_dist[4,1]
  loss4 <- append(loss4,loss)
  loss_agg[i] = loss_agg[i] + loss
}

perc <- c(0.25, 0.5, 0.75, 0.8, 0.85, 0.9, 0.95, 0.98, 0.99, 0.995, 0.999)
Percentile <- c(perc, "Mean", "SD", "Max")
gross1 <- c(quantile(loss1, probs = perc), mean(loss1), sd(loss1), max(loss1))
gross2 <- c(quantile(loss2, probs = perc), mean(loss2), sd(loss2), max(loss2))
gross3 <- c(quantile(loss3, probs = perc), mean(loss3), sd(loss3), max(loss3))
gross4 <- c(quantile(loss4, probs = perc), mean(loss4), sd(loss4), max(loss4))

results.table4 <- data.frame(Percentile, gross1, gross2, gross3, gross4)
kable(results.table4) %>%
  kable_styling(full_width = F)
```

[Previous R Code](/ACTL4001-Supreme/gof) | [Home](/ACTL4001-Supreme) 

